%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.johndang.me/}{\Large John Dang}} & Email : \href{mailto:jamqd@ucla.edu}{jamqd@ucla.edu}\\
  Website: \href{https://www.johndang.me/}{johndang.me} & Phone : +1 (669) 294 3916\\
  San Jose / Los Angeles, CA & Github : \href{https://github.com/jamqd}{jamqd}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Los Angeles}{Los Angeles, CA}
      {Bachelor of Science in Computer Science; Achievement Scholarship Recipient}{Sep. 2018 -- Jun. 2022}
      \resumeItemListStart
        \resumeItem{Relevant Coursework}{
            Algorithms and Complexity, Data Strucrtures and Algorithms, Proof-based Probability Theory,
            Linear Algerbra, Multivariate Calculus, Software Construction, Research, Statistical Reasoning
        }
        \resumeItem{Student Organizations}{
            Association for Computing Machinery (AI Officer), DataRes (Project Manager)
        }
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Center for Vision Cognition Learning and Autonomy \href{https://vcla.stat.ucla.edu/}{(VCLA)}}{UCLA CS and Stats Department}
      {Research Intern}{May 2019 - Present}
      \resumeItemListStart
        \item {Researching reinforcement learning and casual transfer learning including applications in robotics}
        \item {Developing VRGym, a platform for physical and interative AI/robotics research. VRGym 
        enables reinforcement learning research in physically and visually realistic 3D environments.}
      \resumeItemListEnd

    \resumeSubheading
      {Sike AI \href{https://sikeinsights.com/}{(sikeinsights.com)}}{Los Angeles, CA}
      {Deep Learning Engineer }{Oct 2018 - Present}
      \resumeItemListStart
        \item{Developed core deep learning models for five-factor OCEAN personality trait extraction from text,
          audio, and video. On average, my model accurately predicts personality scores within 0.015 (Each 
          personality trait is a real number between 0 and 1.0).} 
        \item {Built data infrastructure. Setup data ingestion and procressing on AWS EC2, S3, and RDS. 
              Ran distibuted deep learning model training across multiple GPUs.}
        \item {Deployed Tensorflow deep learning model on Flask server for use with all Sike products 
              on AWS EBS. Deep learning model is used to provide companies insights to their employees, 
              enabling managers to better onboard and work with new hires.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Ozcan Research Group \href{https://org.ee.ucla.edu/}{(org.ee.ucla.edu)}}{UCLA ECE Department}
      {Machine Learning Researcher (Howard Hughes Medical Institute Project)}{Oct 2018 - Jun 2019}
      \resumeItemListStart
        \item {Developed convolutional neural network for accurate and efficient protein particle analysis 
              used for disease diagnosis. Model can perfrom inference in 0.2 seconds per image on a 
              Raspberry Pi.}
        \item {Presented work at Howard Hughes Medical Institute Undergraduate Research Conference.}
      \resumeItemListEnd

    \resumeSubheading
      {Logos \href{https://logosnews.tech/}{(logosnews.tech)}}{Los Angeles, CA}
      {Software Engineering Intern}{Oct 2018 - Dec 2018}
      \resumeItemListStart
        \item {Developed iOS app for a new crowd-sourced  and personalized news platform in Swift.}
        \item {Developed feature enabling users to highlight lines in articles for social
              interaction with other users.}
        \item {Restructured Firebase database and rewrote NodeJS back-end data processing Google Cloud
              functions enabling faster app loading and performance.}

      \resumeItemListEnd

  \resumeSubHeadingListEnd


% --------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {Python, C++, C, Java, Javascript, Bash, Octave, Matlab, Swift, HTML, CSS}
    \resumeSubItem{Machine Learning / Data Science}
    {Tensorflow, Keras, Numpy, Pandas, Jupyter, SQL, Firebase}
    \resumeSubItem{Amazon Web Services}
    {EC2, S3, RDS, EBS}
    \resumeSubItem{Other Technologies}
    {Git, Github, Docker, LaTeX, Google Cloud Platform, Microsoft Azure }
 \resumeSubHeadingListEnd


 %-----------PROJECTS-----------------
% \section{Projects}
% \resumeSubHeadingListStart
%   \resumeSubItem{Sincerely, AI}
%     {Trained deep learning model that classifies text as sincere or insincere on Quora insincere
%     questions dataset with 96\% accuracy (0.7 F1-score). Deployed model on Django server for 
%     use with custom-built Chrome Extension and Web App interfaces.}
%   \resumeSubItem{Perspective}
%     {Builg Java Web App that alllows for user to read and compare two news articles side by side that 
%     are most likely to differ in perspective. Winner of Most Useful Hack at EV Hacks III.}
% \resumeSubHeadingListEnd



%-------------------------------------------

\end{document}