%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience (Engineering)}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Undergraduate Student Researcher}
    {Center for Vision Cognition Learning and Autonomy (VCLA) / \newline
    International Center for AI and Robot Autonomy Inc. (CARA)} % Organization
    {Los Angeles, CA} % Location
    {May. 2019 - Present} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing VRGym, an AI research platform for training and evaluating agents in
        3D environments \textbf{(Unreal Engine/ROS/C++/Python)} for causal transfer learning and 
        reinforcement learning research projects. VRGym platform will be open-sourced soon.} 
        \item {Designed and implemented automatic structured, stochastic 3D scene generation including integration with Shapenet and Partnet 
        3D model datasets. 
        Wrote scripts for automated import and conversion of raw 3D model files into Unreal Engine assets.}
        \item {Integrating \textbf{Pyro}, a \textbf{Pytorch}-based probabilistic programming language for probabilistic inference in stochastic VRGym environments.}
        \item {Demonstration of VRGym work was presented by Professor Song-Chun Zhu during an invited talk at \textbf{World AI Conference 2019} in Shanghai.}
    \end{cvitems}
    }

  \input{common/sike.tex}

  \cventry
  {Undergraduate Student Researcher}
  {Ozcan Research Group (ORG) / Howard Hughes Medical Institute (HHMI)} % Organization
  {Los Angeles, CA} % Location
  {Oct. 2018 - Jun. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Trained, evaluated, and tuned deep learning models with \textbf{Tensorflow}. Ran 
      experiments to evaluate various research ideas and visualize results.}
      \item Utilized Tensorflow Lite, model weight quantization and various other efficiency optimizations. Optimizations 
      allowed model to run on Raspberry Pi embedded device, meeting hardware constraints and interfacing with 
      previous work in lab on building lens-free mobile microscopes.
    \end{cvitems}
  }

  \input{common/logos.tex}
\end{cventries}
