\cvsection{Projects and Extracurriculars}

\begin{cventries}

    \cventry
    {AI Projects Officer and Project Manager} 
    {UCLA ACM AI Internal Project: DeepFake Detection}
    {}
    {}
    {
      \begin{cvitems} 
        \item UCLA Association for Computing Machinery (UCLA ACM) is UCLA's largest undergraduate computer science 
        student organization. Currently, I am leading one of our internal AI projects.
        \item {Leading a team of UCLA undergraduate students in building systems
        for detecting synthetic images and videos of people. Will submit to Deepfake Detection Challenge in coming months.}
      \end{cvitems}
    }

    \cventry
    {Developer (SB Hacks 2019)} % Role
    {Sincerely, AI} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Trained \textbf{Tensorflow} deep learning model for detection of insincere questions using 
        NLP. Achieved \textbf{96\% accuracy and 0.7 F1-score} on Quora Insincere 
        Questions Dataset (over 1.3 Million data samples). Utilized transfer learning and model hyperparameter fine-tuning.}
        \item {Deployed model on Django web server for use with Chrome Extension that determines
        sincerity of highlighted text on webpage \textbf{(Python)}.}
      \end{cvitems}
    }

  \cventry
    {Developer (EV Hacks II)} % Role
    {Perspective} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed \textbf{Java} web app that allows user to read two news articles side by side 
        that are likely to differ in perspective on the user's search query. }
        \item{Integrated Bing News Search API for article retrieval and scraped web for bias data for determining likelihood of articles differing in perspective.}
      \end{cvitems}
    }

\end{cventries}
