%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Undergraduate Student Researcher; Principal Investigator: Professor of CS and Statistics, Song-Chun Zhu} % Job title
    {Center for Vision Cognition Learning and Autonomy (VCLA) / \newline
    International Center for AI and Robot Autonomy Inc. (CARA)} % Organization
    {Los Angeles, CA} % Location
    {May. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researching transfer learning, reinforcement learning, and causal learning jointly at VCLA lab and CARA non-profit under Prof. Song-Chun Zhu.}
        \item {Developing VRGym, an AI research platform for training and evaluating agents in
        3D environments built on on Unreal Engine (C++ and Python). } 
        \item {Desgined and implemented automatic structured, stochastic 3D scene generation including integration with Shapenet and Partnet. 
        Wrote scripts for automated import and conversion of raw 3D model files into Unreal Engine assets. VRGym platform will be open-sourced soon.}
        \item {Integrating Pyro, a Pytorch-based probabilistic programming language for probabilistic inference in stochastic VRGym environments.}
        \item {Demonstration of work was presented by Professor Song-Chun Zhu during part of an invited talk at World AI Conference 2019 in Shanghai.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Deep Learning Engineer} % Job title
    {Sike AI (Anderson Venture Accelerator and StartupUCLA Backed)} % Organization
    {Los Angeles, CA} % Location
    {Oct. 2018 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created deep learning model for five-factor OCEAN personality trait extraction from text for enabling 
        client companies' management to understand employees. Model predicted 0.0-1.0 valued personality traits within 0.015.
        Utilized state of the art natural language processing algorithms.}
        \item {Desgined and implemented data infrastructure, including storage on AWS Simple Storage Service
         and Relational Database Service (MySQL).
        \item Ran multi-GPU distributed Tensorflow model training on AWS Elastic Compute Cloud, and model deployment on AWS Elastic Beanstalk.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Researcher; Principal Investigator: Professor of Electrical Engineering, Aydogan Ozcan} % Job title
    {Howard Hughes Medical Institute (HHMI) / Ozcan Research Group (ORG)} % Organization
    {Los Angeles, CA} % Location
    {Oct. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed deep learning system for quick, mobile, and accurate protein analysis of blood sample images for disease diagnosis in Tensorflow.}
        \item {Custom Convolutional Neural Network system achieved tenfold improvement over traditional methods in efficiency on embedded devices.}
        \item Presented work at Howard Hughes Medical Institute Day Undergraduate Research Conference. Poster here: \href{https://www.johndang.me/ozcan}{www.johndang.me/ozcan}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Logos News LLC.} % Organization
    {Los Angeles, CA} % Location
    {Oct. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed iOS app in for diverse, crowd-sourced, and personalized news platfrom (Swift). Performed various app bug fixes and refractoring.
        \item Implemented article text highlighting feature enabling text-specific social interaction, discussion, and bias ratings.}
        \item Redesigned Firebase database structure and wrote new Google Cloud Functions, lowering data processing and app loading times (Javascript).
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
