\cvsection{Research}

\begin{cventries}

    %---------------------------------------------------------
      \cventry
        {Advisor: Professor Song-Chun Zhu (UCLA Computer Science and Statistics Departments)} % Job title
        {Causal Transfer Learning and Reinforcement Learning} % Organization
        {VCLA Lab at UCLA and CARA Inc.} % Location
        {May. 2019 - Present} % Date(s)
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Working jointly under Center for Vision, Cognition, Learning, and Autonomy (VCLA) lab at UCLA and 
            International Center for AI and Robot Autonomy Inc. (CARA) non-profit corporation. }
            \item {Researching algorithms for getting agents to learn causal relationships in 
            complex environments. Currently exploring novel information-gain, program synthesis, 
            grammar induction, and probabilistic programming approaches for exploration that enables causal discovery.}
            \item {Researching ways to combine causal discovery, causal models, and 
            counterfactual reasoning 
            with reinforcement learning to enable agents to better 
            transfer between multiple different, but related tasks without needing large amounts of data.}
          \end{cvitems}
        }
    
    %---------------------------------------------------------
\end{cventries}

\begin{cventries}

    %---------------------------------------------------------
      \cventry
        {Advisor: Professor Aydogan Ozcan (UCLA Electrical Engineering Department and HHMI)} % Job title
        {Deep Learning for Mobile Medical Microscopy} % Organization
        {Ozcan Research Group / HHMI} % Location
        {Oct. 2018 - Jun. 2019} % Date(s)
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Work on Howard Hughes Medical Institue (HHMI) and National Science Foundation (NSF) project under Ozcan Research Group for 
            capillary force driven bead agglutination flow assay for point of care with lens-free microscopy and deep learning,}
            \item {Developed deep learning system for quick, mobile, and accurate protein particle analysis of blood sample images for disease diagnosis.}
            \item  {Custom Convolutional Neural Network system achieved \textbf{tenfold improvement} over traditional methods in efficiency on embedded devices.}
            \item {Presented poster of work, at Howard Hughes Medical Institute Day Undergraduate Research Conference:
            \\ \textbf{John Dang}, David Wang, Qianwen Zhong, Yi Luo, Hyouarm Joung, Aydogan Ozcan. "Fast Particle Analysis Using Machine Learning," \textit{HHMI Day 2019.}}
          \end{cvitems}
        }
    
    %---------------------------------------------------------
\end{cventries}